---
title: "Heights of Parents and Children Classified by Gender"
author: "Matt Wilchek & Amelia Kelly"
date: "March 3, 2017"
output:
  ioslides_presentation:
    widescreen: true
    transition: slower
    smaller: true
runtime: shiny
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2) # for graphing
library(lattice) # for graphing
library(car) # for grpahing
PearsonLeeData <- read.csv(url("https://raw.githubusercontent.com/mwilchek/IntroToDS_Project1/master/NewPearsonLeeData.csv"))
PearsonLee <- data.frame(PearsonLeeData)
child <- (PearsonLee$child)
parent<- (PearsonLee$parent)
```

## Overview
- Goal
- Background of Dataset
- Research/Background
- Epicycles of Analysis
- Problem Definition (SMART)
- Initial Exploration (Variable Meanings)
- Initial Exploration (Descriptive Statistics)
- Coding Standards (Comments)
- Results/Interpretations
- Conclusions and Next Steps

## Goal (About)

This R Markdown presentation is made to be interactive using a library called 'Shiny'. The viewers of the presentation can change the assumptions underlying what's presented and see the results immediately from their own web browser or by running this R Markdown file. 

About using Shing see: [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

## Interactive Plot (Example)

```{r eruptions}
inputPanel(
  selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20),
  
  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
)

renderPlot({
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser eruption duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})
```

## Initial Exploration (Variable Meanings)

- Child: child height in inches, a numeric vector
- Parent: parent height in inches, a numeric vector
- Frequency: a numeric vector
- GP: a factor with levels fd fs md ms
- Par: a factor with levels Father Mother
- Chl: a factor with levels Daughter Son
```{r echo=FALSE}
str(PearsonLee)
```

## Initial Exploration (Descriptive Statistics)

```{r echo=FALSE}
summary(PearsonLee)
```

## Histograms of Children's and Parent's Heights

```{r echo=FALSE}
par(mfrow=c(1,2))
hist(child,
# freq = NULL, probability = !freq,
# include.lowest = TRUE, right = TRUE,
# density = NULL, angle = 45, col = NULL, border = NULL,
main = paste("Histogram of Children's Heights"),
# xlim = range(breaks), ylim = NULL,
xlab = "Children's Heights", col="darkgreen",
axes = TRUE, plot = TRUE)

hist(parent,
# freq = NULL, probability = !freq,
# include.lowest = TRUE, right = TRUE,
# density = NULL, angle = 45, col = NULL, border = NULL,
main = paste("Histogram of Parent's Heights"),
# xlim = range(breaks), ylim = NULL,
xlab = "Parent's Heights", col="blue",
axes = TRUE, plot = TRUE)
```

## Scatterplot of Children's and Parent's Heights

```{r echo=FALSE}
par(mfrow=c(1,2))
plot(parent, child, main="Scatterplot Example",
   xlab="Child Height ", ylab="Parent Height ", pch=19)

with(PearsonLee, 
    {
    lim <- c(55,80)
    xv <- seq(55,80, .5)
    sunflowerplot(parent,child, number=frequency, xlim=lim, ylim=lim, seg.col="gray", size=.1, main="Sunflowerplot Example", xlab="Child Height", ylab="Parent Height")
    abline(lm(child ~ parent, weights=frequency), col="blue", lwd=2)
    lines(xv, predict(loess(child ~ parent, weights=frequency), data.frame(parent=xv)), 
          col="blue", lwd=2)
    if(require(car)) {
    dataEllipse(parent,child, xlim=lim, ylim=lim, plot.points=FALSE)
        }
  })
```

Through the scatterplots we can see where the concentration of observations lie and the trend of the dataset.

## Box Plots of Child Height vs. Parent Height

```{r echo=FALSE}
par(mfrow=c(1,2.5))

boxplot(child~parent, data=PearsonLee, main="Boxplot of Parent to \nChildren's Height",
xlab="Parent", ylab="Children's Height", col=c('powderblue','mistyrose'))

boxplot(parent~child, data=PearsonLee, main="Boxplot of Children to \nParent's Height",
xlab="Children", ylab="Parent's Height", col=c('mistyrose','powderblue'))
```
